Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-04-24 Ben_Manuscripts/structure_paper/Outline.tex
Edits and new figures

  \subsection*{Determination of Nanoscopic Structural Details}

@@

  We will now address the questions raised in the introduction in the order
  that they were asked.  %BJC: Not a fan of this transition

@@

  The simulations best support a model built with 5 monomers per layer based on 
  the measured pore-to-pore distances. To discern the composition of the monomer 
  layers, addressing (\ref{point:monomernum}), we ran simulations of systems created
  with 4 - 8 monomers per layer.  % BJC: can't figure out how to word this : should be 'with between 4 and 8 monomers' or 'with from 4 to 8 monomers'?
  \begin{itemize}
        \item We created systems in both the parallel displaced and sandwiched configurations
	\item All systems were prepared according to the dry equilibration procedure
        \item All systems are stable after 400 ns of simulation.  
        \item Figure ~\ref{fig:p2p} shows the pore spacing for all systems tested.
        \item Systems built with 5 monomers in each layer equilibrate to a pore spacing
        that is most consistent with the experimental value of 4.12 nm derived from
        SAXS measurements (Figure~\ref{fig:SAXS}).
        \item The remainder of this discussion will focus on the analysis of systems
        built with 5 monomers per layer.
  \end{itemize}

  %BJC: maybe split into 2 paragraphs
  %MRS2: usually good instinct.  Lead with the conclusions of the research you are trying to convince readers. Rather than phrasing as a question. Something like: ``Layers are well defined and persistent''. 
  We learned that layers are well-defined and persistent, answering (\ref{point:layers})
  %We verified that the system stays partitioned into layers by
  We verified our conclusion by
  plotting the pair correlation function, $g(z)$ calculated between atoms along
  the length of the pores (Fig~\ref{fig:zdf}).
  \begin{itemize}
	\item We measured $g(z)$ with respect to aromatic rings in the head groups
	and, separately, with respect to carbon atoms on the alkane chains.
	% \item In both cases, we see a degree of layer partitioning
        \item Using the head groups as reference, we see that sandwiched configuration
	layers stack 4.29 \angstrom apart while parallel displaced configuration layers
	stack 4.37 \angstrom apart.
	\item Using the alkane chain carbons as reference we see a layer spacing of 4.39 \angstrom
	and 4.38 \angstrom in the sandwiched and parallel displaced configurations respectively.
        \item The power spectrums used to calculate the reported layer spacings are given in the 
        Supplemental Information.  %BJC: "Power spectrum" an okay description here?
	% BJC: TODO: Overlay plots of tail and headgroup densities
        %MRS2: repore more precisely what finding is interesting. What does that difference mean?
%	\item We see a difference in the spacing in the head group versus tail region
%	because there is more volume to fill with less densely packed carbon chains in the tail region. 
	% BJC: vvv Need to get the same information for the tail zdfs.
%	\item Even though the layer spacing is similar, the sandwiched configuration
%	exhibits more defined layers with its first peak deviating from the mean 
%        number density by 61 \%. %BJC: I mention how I do this calculation in the methods. Is it clear that I'm doing that here?
%MRS2: fine for description for now.          
%	\item The parallel displaced configuration deviates from the mean by only 
%	12 \% in comparison.
%MRS2: is this that unexpected, since parallel displaces should have layers that alternate anyway?
%BJC: true, but I'm just stating the facts
  \end{itemize}

  \begin{figure}
        \centering
        \begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{zdf5layered.png}
                \caption{}\label{fig:zdf_layered}
        \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{zdf5offset.png}
                \caption{}\label{fig:zdf_offset}
        \end{subfigure}
        \caption{Pair distribution functions of aromatic carbons for the
        (a) 5 monomer per layer, sandwiched and (b) 5 monomer per layer,
        parallel displaced configurations. Clear periodic maxima in the
        $z$ probability density indicate distinct layers. The magnitude
        of the spikes with respect to the average suggest that the 5
        monomer per layer, sandwiched configuration possesses a higher
        degree of layer partitioning.}\label{fig:zdf}
  \end{figure}

  % BJC: Even though I will shift focus to only 5 monomers per layer, I will put other data
  % such as XRD of 4, 6, 7, 8 mon/layer in supplemental information 
  %MRS2: good.
  \begin{figure}
	\centering
	\includegraphics[width=0.5\linewidth]{p2p.png}
	\caption{The pore spacing (given in nm) of the model increases as
	number of monomers in each layer increases. The pore spacing of a system
	starting in the sandwiched configuration is systematically lower than 
	that started in an offset configuration. Systems built with 5 monomers
	per layer in a parallel displaced configuration result in a pore spacing
	closest to the experimental 4.12 nm}~\label{fig:p2p}
  \end{figure}

%  \begin{table}[h]
%  \centering
%  \begin{tabular}{ccc}
%  \toprule
%  		   & \multicolumn{2}{c}{Starting Configuration} \\
%  \hline
%  Monomers per layer & Sandwiched & Parallel Displaced \\
%  \midrule
%  4 & $3.72 \pm 0.04$ & $3.84 \pm 0.02$ \\  % done
%  5 & $4.20 \pm 0.04$ & $4.23 \pm 0.04$ \\
%  6 & $4.69 \pm 0.04$ & $4.72 \pm 0.03$ \\
%  7 & $4.66 \pm 0.02$ & $4.82 \pm 0.03$ \\  % done
%  8 & $5.00 \pm 0.04$ & $5.33 \pm 0.02$ \\
%  \bottomrule
%  \end{tabular}
%  \caption{The pore spacing (given in nm) of the model increases as
%  number of monomers in each layer increases. The pore spacing of a system
%  starting in the sandwiched configuration is systematically lower than 
%  that started in an offset configuration. Systems built with 5 monomers
%  per layer in a parallel displaced configuration result in a pore spacing
%  closest to the experimental 4.12 nm}
%  \label{table:p2p} 
%  \end{table}

>>>>

%  \subsection*{Determination of Nanoscopic Structural Details}

@@

 % We will now address the questions raised in the introduction in the order
  %that they were asked.  %BJC: Not a fan of this transition

@@

  %BJC3: Feel free to suggest different words
  \subsection{Density of monomers around pores}
  Our simulations best support a model built with 5 monomers per layer based on
  the measured equilibrated pore-to-pore distances. To discern the composition of
  the monomer layers, addressing question (\ref{point:monomernum}), we ran
  simulations of systems created with 4--8 monomers per layer. 
  \begin{itemize}  
  		\item We built systems in both the parallel displaced and sandwiched configurations 			with layers initially spaced 3.7 \AA~apart according to the dry equilibration 
  		procedure.
  		\item The pore-to-pore spacing is stable in all systems are stable after 400 ns of 
  		simulation. Figure~\ref{fig:p2p} shows the equilibrated pore-to-pore distances for all 
  		systems tested. 
  		\item Systems built with 5 monomers in each layer equilibrate to a pore spacing that is 
  		most consistent with the experimental value of 4.12 nm derived from SAXS measurements 
	    (Figure~\ref{fig:SAXS}).
  \end{itemize}

  %  The simulations best support a model built with 5 monomers per layer based on 
%  the measured pore-to-pore distances. To discern the composition of the monomer 
%  layers, addressing (\ref{point:monomernum}), we ran simulations of systems created
%  with 4 - 8 monomers per layer.  % BJC: can't figure out how to word this : should be 'with between 4 and 8 monomers' or 'with from 4 to 8 monomers'?
%  \begin{itemize}
%        \item We created systems in both the parallel displaced and sandwiched configurations
%	\item All systems were prepared according to the dry equilibration procedure
%        \item All systems are stable after 400 ns of simulation.  
%        \item Figure ~\ref{fig:p2p} shows the pore spacing for all systems tested.
%        \item Systems built with 5 monomers in each layer equilibrate to a pore spacing
%        that is most consistent with the experimental value of 4.12 nm derived from
%        SAXS measurements (Figure~\ref{fig:SAXS}).
%        \item The remainder of this discussion will focus on the analysis of systems
%        built with 5 monomers per layer.
%  \end{itemize}

  The remainder of this discussion will focus on the analysis of systems built with
  5 monomers per layer. 
  \begin{itemize}
	  	\item Systems built with 6 monomers per layer have an equilibrated
  		pore spacing c.a. 0.50 nm higher than experiment. 
  		\item Systems built with 4 monomers per layer equilibrate to a pore spacing 0.25 nm 
  		lower than experiment. 
  		\item In a sense, all systems tested are at least metastable, however not all will make 
  		physical sense or fit the experimental profile that we are trying to match.
  		\item In the limit of infinite simulation time, all simulations will converge to a 	
  		single density.
  		\item It is our intention to choose an initial configuration which quickly reaches a 
  		monomer density close to experiment.
  \end{itemize}

  \begin{figure}
	\centering
	\includegraphics[width=\linewidth]{p2p.png}
	\caption{Systems with 5 monomers per layer have equilibrated pore spacings closest to
			 the experimental value of 4.12 nm. The equilibrated pore spacing of the model 	
			 increases as the number of monomers in each layer increases. The pore spacing
			 of systems starting in the sandwiched configuration are systematically lower
			 than those started in the parallel displaced configuration.}~\label{fig:p2p}
  \end{figure}

% BJC3: replaced by plot above.
%  \begin{table}[h]
%  \centering
%  \begin{tabular}{ccc}
%  \toprule
%  		   & \multicolumn{2}{c}{Starting Configuration} \\
%  \hline
%  Monomers per layer & Sandwiched & Parallel Displaced \\
%  \midrule
%  4 & $3.72 \pm 0.04$ & $3.84 \pm 0.02$ \\  % done
%  5 & $4.20 \pm 0.04$ & $4.23 \pm 0.04$ \\
%  6 & $4.69 \pm 0.04$ & $4.72 \pm 0.03$ \\
%  7 & $4.66 \pm 0.02$ & $4.82 \pm 0.03$ \\  % done
%  8 & $5.00 \pm 0.04$ & $5.33 \pm 0.02$ \\
%  \bottomrule
%  \end{tabular}
%  \caption{The pore spacing (given in nm) of the model increases as
%  number of monomers in each layer increases. The pore spacing of a system
%  starting in the sandwiched configuration is systematically lower than 
%  that started in an offset configuration. Systems built with 5 monomers
%  per layer in a parallel displaced configuration result in a pore spacing
%  closest to the experimental 4.12 nm}
%  \label{table:p2p} 
%  \end{table}

  \subsection{Structural determination}

  We further refined our structural understanding of the system by simulating X-ray 
  diffraction patterns produced from equilibrated MD trajectories and comparing them
  to experiment. 
  \begin{itemize}
	  	\item We tested systems built with 5 monomers per layer in the parallel 
		displaced and sandwiched configurations at 300K.
		\item We generated simulated patterns using portions of simulation trajectory
		after equilibration.
		\item The patterns for both structures are shown and compared to experiment
		in Figure~\ref{fig:XRDsim}.
  \end{itemize}

%  Simulated XRD of the sandwiched configuration contains all experimental
%  features except for R-helix. R-alkanes, R-spots and R-pores appear close to their
%  expected locations. R-$\pi$ is also present, however it intersects R-alkanes at
%  a $q_z$ value lower than experiment meaning the head groups in our model prefer 
%  to stack farther apart.

%  Like the sandwiched configuration, the parallel displaced configuration creates
%  a simulated XRD pattern with all major experimental reflections except for R-helix.
%  R-alkanes and R-pores appear as they do in the sandwiched configuration. R-spots
%  and R-$\pi$ appear, however with a lower intensity
%  relative to R-alkanes when compared to the sandwiched configuration. R-helix
%  appears due to the parallel displaced aromatic rings. It is a subharmonic of
%  R-$\pi$ since the nearest vertically stacked head group to any given head group
%  is $2\times$R-$\pi$~away. 
% BJC: adjust figure size and alignment -- probably easiest to set figure size in matplotlib

% BJC3: update with 300K pics. Presented separately from 280K for now. 
  \begin{figure}
  \begin{subfigure}{0.3\linewidth}
        \centering
        \vspace{-0.2em}
        \includegraphics[width=1.1\linewidth,trim={1cm 0 1.3cm 0},clip]{rzplot_offset_300K.png}
        \caption{}~\label{fig:rz_offset}
  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
        \centering
%        \vspace{0.25em}
        \includegraphics[scale=0.285]{WAXS_raw.png}
        \caption{}~\label{fig:raw_waxs}
  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
        \centering
        \includegraphics[width=1.1\linewidth,trim={1cm 0 1.3cm 0},clip]{rzplot_layered_300K.png}
        \caption{}~\label{fig:rz_layered}
  \end{subfigure}
  \begin{subfigure}{0.0544\linewidth}
        \centering
        \vspace{-4.00em}
        \includegraphics[width=\linewidth]{colorbar_seismic.png}
  \end{subfigure}
%MRS6: question: the SAXS region looks different between sandwiched and parallel displaced. Any thoughts why? We can discuss in person.  And seems like have to comment on the difference in intensity between Sandwich and parallel displaced in the pi-pi region.
%MRS6: I wonder to what extent showing the reflections of tails removed would make it clearer pi-pi is really there.  Maybe in supporting info?
%BJC2: Sure, I'll add that to supporting info
  \caption{The simulated XRD pattern generated from the equilibrated trajectory
	  of the parallel displaced configuration (a) exhibits all major reflections
	  present in the experimental WAXS pattern (b). The simulated XRD pattern
	  generated from the equilibrated trajectory in the sandwiched configuration (c) shows
	  all major reflections except R-helix.}
  \label{fig:XRDsim}
  \end{figure}

  The simulated XRD patterns produced from both systems show moderate qualitative 
  agreement with experiment. 
  \begin{itemize}
  		\item R-alkanes and R-pores appear in the expected location
		\item R-pores is more intense than experiment, likely because we are simulating a 
		perfect, infinite hexagonal array. The real system has defects and domain misalignment
	    which decreases the overall intensity.
	    \item R-$\pi$ appears at a lower $q_z$ value than experiment. In both systems, the
	    reflection reaches its maximum at c.a. $q_z=1.4$ which means that monomers prefer 
	    to stack c.a. 4.5 \AA apart rather than 3.7 \AA. This behavior is not surprising since
	    GAFF models atoms as point charges and does not appropriately model the aromatic
	    $\pi-\pi$ interactions which would cause the monomers to stack closer together.
	    \item R-spots is missing in both places, at least visually. The tails in our model
	    are more disordered than the experimental system at 300K.  
	    \item R-helix does not appear in either case.
  \end{itemize}

  The simulated XRD pattern of the parallel displaced configuration shows an additional
  reflection due to its helical structure. 
  \begin{itemize}
  		\item There are horizontal reflections at $|q_z|= 0.7 \AA^{-1}$, exactly half of 
  		the $q_z$ value of R-$\pi$. 
  		\item The reflection does not cross through $q_r = 0 \AA^{-1}$ so it does not
  		appear for the same reason as R-helix. 
  		\item It is possible that these reflections contribute to the continuation of
  		R-helix into R-alkanes, as seen in the experimental pattern. 
  \end{itemize}

  There are numerical discrepancies between the relative intensities of each reflection when
  comparing experimental and simulated patterns.
  \begin{itemize}
  		\item Table~\ref{table:relative_inensities_300K} quantifies the relative intensity
  		of each reflection.
  		\item The intensity of R-spots is much lower than experiment (need to update the numbers in that table with 300K results)
  		\item There is no R-helix intensity
  		\item R-$\pi$ is nearly an order of magnitude higher in our simulations
  		compared to experiment.
  \end{itemize}

  \begin{table}[h]
  \centering
  \begin{tabular}{cccc}
  \toprule
  		   & \multicolumn{3}{c}{Configuration} \\
  \hline
  Reflection & Experiment & Sandwiched & Parallel Displaced \\
  \midrule
  R-alkanes & 1.0 &  1.0 &  1.0  \\  
  R-$\pi$   & 2.8 & 18.0 & 14.0  \\
  R-spots   & 1.5 &  1.6 &  1.2  \\  % Need to get these actual data points
  R-helix   & 0.9 &  --  & --    \\ 
  \bottomrule
  \end{tabular}
  \caption{The relative intensities of reflections of interest}
  \label{table:relative_inensities_300K} 
  \end{table}

%  The simulated XRD pattern produced from the sandwiched configuration is missing
%  R-helix and R-spots. 
%  \begin{itemize}
%		\item R-pores and R-alkanes appear in their expected locations. 
%		\item R-pores is more intense than experiment, likely because we are simulating a 
%		perfect, infinite hexagonal array. The real system has defects and domain misalignment
%	    which decreases the overall intensity.
%	    \item R-$\pi$ appears with a very high intensity and is shifted down to a lower value
%	    of $q_z$ meaning monomers in our model prefer to stack farther apart.  
%	    \item R-spots may be faintly present, however it is not present to the degree shown
%	    experimentally. (see table with relative intensities) 
%  \end{itemize}

  %BJC: discussed parallel displaced and sandwiched configs in separate paragraphs to 
  % avoid confusion. Need to make thesis less dry. 
%  The simulated XRD pattern generated from the parallel displaced configuration is also
%  missing R-helix and R-spots.
%  \begin{itemize}
%  		\item R-pores and R-alkanes appear in the expected location again
%  		\item R-$\pi$ is present in the same location as the sandwiched configuration with
%  		high intensity. 
%  		\item R-helix is not present, however off-axis reflections appear at the same value 
%  		of $q_z$ where we expect to see R-helix. These appear since there is a helical 
%  		arrangement of monomers in the parallel displaced configuration. A helix alone will
%  		not give rise to a reflection at $q_r = 0$ (See supporting info for demonstration)
%  		\item There is elevated intensity where we expect to see R-spots, however it cannot
%  		be easily distinguished from the higher intensity arcs which overlay the top and 
%  		bottom of R-alkanes.
%  \end{itemize}

%  The simulated diffraction patterns indicate that there is something going wrong
%  with the way the system is modeled. We must address all of these issues and justify
%  their occurrence.
  There are clear differences between our simulated results and experimental results
  that must be addressed and justified. We will explore the origin of each experimental 
  reflection and hypothesize why they do not appear in our simulated patterns. Specifically,
  we want answer:  
  %BJC: I could number these and answer them individually
  \begin{enumerate}
	\item What is the origin of R-spots?
  	\item Why is the intensity of R-$\pi$ so much greater than experiment?
  	\item What is the origin of R-helix?
  \end{enumerate}

  \subsubsection{Origin of R-spots}

  We observed R-spots when we ran simulations of each system at 280K. (figure to be added - include with 300K patterns or keep separate??)
  \begin{itemize}
  		\item R-spots is most intense in the sandwiched configuration
  		\item Still no R-helix
  \end{itemize}

  %BJC: might be able to combine with other table
  \begin{table}[h]
  \centering
  \begin{tabular}{cccc}
  \toprule
  		   & \multicolumn{3}{c}{Configuration} \\
  \hline
  Reflection & Experiment & Sandwiched & Parallel Displaced \\
  \midrule
  R-alkanes & 1.0 &  1.0 &  1.0  \\  
  R-$\pi$   & 2.8 & 27.0 & 119.0  \\
  R-spots   & 1.5 &  1.6 &  1.2  \\  
  R-helix   & 0.9 &  --  & --    \\ 
  \bottomrule
  \end{tabular}
  \caption{The relative intensities of reflections of interest}
  \label{table:relative_inensities_300K} 
  \end{table}

  %BJC3: following taken from draft.tex
  The R-spots signal, which appears in both simulated XRD patterns, is not a
  result of alkane chain tilt. Previous literature has attributed the spots in
  this particular WAXS pattern as the product of tilted alkane
  chains~\cite{feng_scalable_2014}. We looked closer at the sandwiched
  configuration since R-spots appears with the most strength in its simulated XRD
  pattern. We measured the tilt angle of the alkane chains and showed that our
  system equilibrates to an average tilt angle close to zero degrees
  (Fig.~\ref{fig:tilt}).

  %BJC3: from draft.tex  
  To understand the origin of R-spots, we determined which
  atoms gave rise to the feature. Since R-spots is present as higher intensity
  spots within R-alkanes, it is likely that the spots arise as a consequence of
  the tails. By removing all non-tail atoms from the trajectory and simulating a
  diffraction pattern, we were able to isolate the cause of the spots to the
  tails (Figure~\ref{fig:tails}). Since the tails stay nearly flat, we plotted
  the centroids of the tails and measured the angle between each centroid and its
  nearest neighbors with respect to the plane of the membrane.  We see distinct
  peaks in the distribution of these angles (Figure~\ref{fig:tail_packing}).

  \begin{figure}
  \centering
  \includegraphics[width=0.5\linewidth]{tilt_dist.png}
  \caption{We measured the angle made between each monomer alkane tail and the
	  membrane plane. The average tilt angle is near 7\degree~which is far from the
	  37\degree~tilt angle previously used to explain R-spots.}~\label{fig:tilt}
  %MRS6: might want to add some discussion about how the angles are also very spread out, so there should be little signal due to tilt anywhere.
  %BJC2: good idea
  \end{figure}

  The peaks in the nearest neighbor angle distribution are consistent with the
  location of R-spots. The peaks of interest in Figures \ref{fig:offset_tails}
  and \ref{fig:layered_tails} are located at $\pm 33 \degree$ which is the same
  location where the highest intensity of spots are located on the simulated
  patterns. We confirmed this conclusion by radially integrating the 2D WAXS
  pattern for $\left|\mathbf{q}\right|$ values between 1.4 and 1.57 (between 4
  and 4.5 \AA~in real space). We observe that distinct peaks appear ca. $30
  \degree$, in close agreement with the previously measured angle distribution
  (Figs.~\ref{fig:offset_integration}~and~\ref{fig:layered_integration}). We
  performed the same integration on the raw experimental data and found the angle
  at which R-spots reaches its highest intensity to be $\pm 37 \degree$ which
  is a reconcilable difference with our simulated results.

%  The evidence supports the hypothesis that alkane chain tails pack in a
%  hexagonal array. Groups of three tails associated with each monomer prefer to
%  sit between tails of vertically stacked monomers rather than stacking directly
%  on top of them (Figure~\ref{fig:hex_tails}). This type of packing has been seen
%  before in XRD studies of hydrocarbon chains~\cite{small_lateral_1984}.

  \begin{figure}
	\centering
	\begin{subfigure}{0.45\linewidth}
		\centering
	 	\vspace{-2em}
		\includegraphics[width=\textwidth]{tails_topview.png}  % picture of top of unit cell with only tail atoms shown
		\caption{}\label{fig:topdown_tails_only}
	\end{subfigure}
	\begin{subfigure}{0.45\linewidth}
		\centering
		\includegraphics[width=\textwidth]{tails_rzplot.png}
		\caption{}\label{fig:tails_rzplot}
	\end{subfigure}
	\caption{(a) We removed all atoms except carbon atoms that constitute the tails from a 
	sandwiched configuration trajectory. (b) The simulated XRD pattern of the
        tail-only trajectory still shows R-spots}\label{fig:tails}
  \end{figure}

  \begin{figure}[!htb]
  \centering
  	\begin{subfigure}{\linewidth}
	\centering
		\begin{subfigure}{0.45\textwidth}
        		\centering
        		\includegraphics[width=\linewidth]{offset_tail_packing.png}
        		\caption{}~\label{fig:offset_tails}
		\end{subfigure}
		\begin{subfigure}{0.45\textwidth}
		\centering
	        	\includegraphics[width=\linewidth]{offset_angle_v_I.png}
		        \caption{}~\label{fig:offset_integration}
		\end{subfigure}
	\end{subfigure}
	\begin{subfigure}{\linewidth}
	\centering
		\begin{subfigure}{0.45\textwidth}
	        \centering
		        \includegraphics[width=\linewidth]{angles_traj_layered.png}
		        \caption{}~\label{fig:layered_tails}
		\end{subfigure}
		\begin{subfigure}{0.45\textwidth}
        	\centering
		        \includegraphics[width=\linewidth]{layered_angle_v_I.png}
		        \caption{}~\label{fig:layered_integration}
		\end{subfigure}
	\end{subfigure} 
    \caption{We hypothesize that R-spots is the result of ordered tail packing.
	  Defining the membrane plane to be 0\degree, we measured the angles between each
	  alkane chain tail centroid and its nearest neighbor centroids for the
	  equilibrated parallel displaced (a) and sandwiched (c) configurations. Peaks
	  that appear in each distribution are centered near $\pm~33\degree$. We radially
	  integrated the simulated XRD patterns of the parallel displaced and sandwiched
	  configuration within the region bounding R-alkanes ((b) and (d) respectively).
	  Peaks appear in the same location as the angle distributions which corroborates
	  our hypothesis. Further, we note that the peaks are strongest in both plots
	  associated with the sandwiched configuration. As shown in Figure
	  \ref{fig:rz_layered}, systems simulated in the sandwiched configuration exhibit
	  more intense R-spots reflections. Note that plots of integrated intensity are
	  normalized so the average alkane intensity (excluding reflections $\pm
	  30\degree$ from the $q_z$ axis) is set to 1.  Plots are cut off for intensities
	  greater than 2 so peaks are more visible.}~\label{fig:tail_packing}
  \end{figure}

  There are a couple reasons why we see ordered chain packing at 280 K and not at the
  experimental conditions of 300 K.
  \begin{itemize}
  		\item (1) The difference between 280K and 300K is small. Our forcefield parameters
  		may not correctly model the behavior of the tails at 300K (citation?).
  		\item (2) Monomers aren't as confined at 300 K in our simulations versus experiment.
  		If the head groups packed 3.7 \AA apart, the tails would be more confined and forced
  		to pack between vertically adjacent monomer tails. In our case, the tail region is
  		less dense than experiment which gives the tails freedom to organize in a more
  		entropically favored disordered state. 
  \end{itemize}

% BJC3 : old outline
% R-spots, which appears in both simulated XRD patterns, is a result of the way 
%  alkane tails pack together.
%  	\item Previously, the spots in the diffraction pattern had been explained 
%	as the product of tilted alkane chains. % BJC: reference 2014 ACS nano paper
%	\item We measured the tilt angle of the alkane chains and showed that our 
%	system equilibrates to an average tilt angle close to zero degrees ~\ref{fig:tilt} % Could belong in supplemental. Leaving here for now 
%	\item To understand the origin of the spots, we determined which atoms gave rise to the feature
%	\item Since R-spots is present as higher intensity spots within R-alkanes, it is likely
%        that the spots arise as a consequence of the tails. 
%	\item By removing atoms from the trajectory and simulating a diffraction 
%	pattern, we were able to isolate the cause of the spots to the tails (Figure~\ref{fig:tails}).
%	\item Since the tails stay nearly flat, we plotted the centroids of the 
%	tails and measured the angle between each centroid and its nearest neighbors
%	with respect to the plane of the membrane (Figure~\ref{fig:centroids}).  %BJC: at one point Matt mention doing a correlation function instead of just measuring the angles
%	\item We see distinct peaks in the distribution of these angles (Figure~\ref{fig:tail_packing})
%  \begin{figure}
%  \includegraphics[width=0.5\linewidth]{tilt_dist.png}
%  \caption{The tilt angle distribution of alkane chain tails with respect to the membrane plane
%  indicates an average tilt angle near 7\degree which is far from the 37\degree tilt angle 
%  previously used to explain R-spots}~\label{fig:tilt}
%  The peaks in the tilt angle distribution are consistent with the location of R-spots.
%	\item The peaks of interest in Figures~\ref{fig:offset_tails}~and~\ref{fig:layered_tails}
%	are located at $\pm$ 33 $\degree$ which is the same location where the highest intensity
%	of spots are located on the simulated patterns
%	\item We confirmed this conclusion by radially integrating the 2D WAXS pattern for q values
%	between 1.57 and 1.4 (real space between 4 and 4.5 \AA) 
%	\item We observe that distinct peaks appear c.a. 30 $\degree$, in close agreement with the
%	previously measured angle distribution (~\ref{fig:offset_integration}~\ref{fig:layered_integration})
%%	\item We integrated the raw experimental 2D WAXS data in the region bounding R-alkanes 
%	\item We performed the same integration on the raw experimental data and found the angle
%	at which R-spots reaches its highest intensity to be $\pm$ 37 $\degree$ which is a 
%	reconcilable difference with our simulated results.  
%  \begin{figure}
%	\begin{subfigure}{0.45\linewidth}
%		\includegraphics[width=\textwidth]{tails_topview.png}  % picture of top of unit cell with only tail atoms shown
%		\caption{}\label{fig:topdown_tails_only}
%	\begin{subfigure}{0.45\linewidth}
%		\includegraphics[width=\textwidth]{tails_rzplot.png}
%		\caption{}\label{fig:tails_rzplot}
%	\caption{(a) All atoms except carbon atoms making up the tails are removed from the 
%	trajectory. (b) The simulated diffraction pattern of the tail-only trajectory still 
%        shows R-spots}\label{fig:tails}
%        %MRS2: might need to say how the dynamic range is adjusted here with only tails, since otherwise people will be confused with the R-spots being more intense. 
%	%BJC: what do you mean by dynamic range?
%	%BJC: Explain how colorbar is adjusted
%  \begin{figure}
%  	\begin{subfigure}{\linewidth}
%		\begin{subfigure}{0.45\textwidth}
%        		\includegraphics[width=\linewidth]{offset_tail_packing.png}
%        		\caption{}~\label{fig:offset_tails}
%		\begin{subfigure}{0.45\textwidth}
%	        	\includegraphics[width=\linewidth]{offset_angle_v_I.png}
%		        \caption{}~\label{fig:offset_integration}
%	\begin{subfigure}{\linewidth}
%		\begin{subfigure}{0.45\textwidth}
%		        \includegraphics[width=\linewidth]{angles_traj_layered.png}
%		        \caption{}~\label{fig:rz_layered}
%		\begin{subfigure}{0.45\textwidth}
%		        \includegraphics[width=\linewidth]{layered_angle_v_I.png}
%		        \caption{}~\label{fig:layered_integration}
%%MRS: 
%  \caption{The distribution of angles w.r.t. the xy plane between alkane chain tail centroids and nearest
%  neighbor centroids for equilibrated parallel displaced (a) and sandwiched (c) configurations. The
%  same peaks are visible when the 2D simulated diffraction data is radially integrated in the R-alkanes region,
%  (b) and (d) respectively.}~\label{fig:tail_packing}
%%MRS2: not clear what the difference is between right and left side figures.
%%BJC: That's good! One is angles measured between tail centroids and the other is radial integration of the simulated xrd patterns. I'll try make that more clear in the caption.
%%MRS3: sorry, I meant to say not clear what the SOURCE of the data is in right vs. left.  Make sure colors and labels are consistent in final 
%%MRS: not clear why some are angles with x axis, and some are angles w neighbors?  Shouldn't it be the same thing plotted in both graphs?
%%BJC: I just need to get the labels right, they are the same thing technically

  \subsubsection{Discrepancies between R-$\pi$}

  We plotted the one-dimensional pair distribution function, $g(z)$, for the centers
  of mass of monomer phenyl rings (Figure reference).
  \begin{itemize}
  		\item We averaged all 1D slices in the z-direction of the full 3D correlation function
  		within 2.1 \AA of $(x, y)=(0, 0)$. (full description will be in methods)
  		\item We chose 2.1 \AA as a crude approximation of the radius of the phenyl ring
  		plane. 
  		\item We calculated it as the sum of the longest C-C distance within a phenyl 
  		ring (2.8 \AA) and two times the carbon atom radius (0.7 \AA).
  \end{itemize}

  The correlation length between stacked monomer head groups shows the best agreement with
  experiment for systems simulated at 300K.
  %BJC3: explanation of correlation length calculation in methods section. 
  \begin{itemize}
  		\item Correlation length was calculated by fitting a decaying exponential function
  		to all peaks of $g(z)$ for the sandwiched configuration and to every other peak of
  		$g(z)$ for the parallel displaced configuration. 
  		\item The correlation length of systems simulated at 280K were 27.7 \AA and 25.2 \AA
  		for the parallel displaced and sandwiched configurations respectively. 
  		\item The correlation length of systems simulated at 300K were 11.2 \AA and 14.9 \AA
  		for the parallel displaced and sandwiched configurations respectively. 
  		\item Systems simulated at 300K show correlation closest to the experimental 
  		correlation length of 10.1 \AA. They are still slightly more correlated than 
  		experiment which would lead to an increase in constructive X-ray scattering. 
  \end{itemize}

  Additionally, our system models near-perfectly straight pores with no defects which will
  lead to higher intensity vertical stacking reflections. 
  \begin{itemize}
  		\item Nearly all of the intensity in R-$\pi$ of our simulated patterns is concentrated
  		at a single point. Figure Something shows the same simulated patterns with the upper 
  		boundary on the colorbar adjusted to be 10x higher. The only visible reflections are
  		those of R-$\pi$.
  		\item In the experimental pattern, the intensity is more evenly spread out over all
  		of R-$\pi$. 
  \end{itemize}

  \subsubsection{Origin of R-helix}

  R-helix will not show up in any of the models tested so far.
  \begin{itemize}
        \item All monomers used to build initial configurations are identical. There is no way 	
        to produce R-helix without a more complex initial configuration 
        \item We calculated the structure factor of simple systems that mimic the parallel
        displaced and sandwiched configurations. Neither give rise to R-helix.
        (See Figure "fourier transforms of simple systems").
        \item The reflection implies a vertical modulation in electron density every 7.4 \AA.                
        \item This modulation can occur in either the head or the tails
        \item There is a not a unique solution to this problem, however we can speculate based
        on what makes the most physical sense.
  \end{itemize}

  We can produce R-helix if our initial configuration contains alternating parallel and
  antiparallel carboxylate groups relative to the plane of the monomer's phenyl ring.
  (Figure reference).  
  \begin{itemize}
  		\item It is difficult to physically justify this system. 
  		\item Systems built this way are only stable if position restraints are placed on 
  		all head group heavy atoms. Carboxylate groups quickly revert to the parallel
  		position as restraints are released.
  		\item There is an appreciable energy barrier that prevents rotation
  		of carboxylate groups attached to phenyl rings since the group extends the system's 
  		$\pi$ conjugation. (citation)
  		\item There are instances where carboxylates in other systems rotate out of plane.
  		\item Bushey et al. showed that bulky carbonyl-containing substituents of stacked arene
  		molecules tended to tilt 45$\degree$ in order to relieve steric strain, thus allowing 
  		$\pi$-stacking between molecules, and to hydrogen bond with neighboring molecules. 
  		\item Lorenzo and Gra\~{n}a found 3 stable dimers of gallic acid (from which the 
  		monomer, NA-GA3C11 was derived) with adenine. In all cases, the carboxylate group 
  		remained planar, even with evidence of hydrogen bonding between the carboxyl group
  		and nitrogen atoms of adenine. 
  		\item The monomers which we are studying have no opportunities to hydrogen bond and 
  		are confined so that any rotation about the phenyl-carboxylate bond would be sterically
  		hindered. 
  \end{itemize}

  We can also produce R-helix if layers are not uniformly spaced. Rather, monomers might form 
  pairs that stack less than 3.7 \AA apart, and whose center of masses are spaced 7.4 \AA 
  from the next pair of monomers.(Figure reference)
  \begin{itemize}
  		\item To our knowledge, there have been no studies that specifically address the 
  		possibility of a configuration like this. 
  		\item Our forcefield causes our system to tend towards uniformly spaced layers. 
  		\item As expected, simulations of this type of system are only stable if position
  		restraints are applied to heavy atoms of the phenyl rings.
  		\item Many \textit{ab initio} studies have measured the equilibrium distance between
  		dimers of benzene and substituted benzene.
  		\item Tauer and Sherrill explored the binding energies of tetramers of benzene, but
  		did not explore the report the equilibrium distance between benzene rings. 
  		\item Even if there have been other studies of the equilibrium distance between 
  		stacks of benzene rings, it still does not model our system which has many 
  		electron-withdrawing groups and bulky substituents that would likely affect stacking
  		preferences. 
  \end{itemize}
